Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation

### 2022-01-12 paper/paper.Rmd
edit slope methods
minor edits

---
title: "Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation"
author: "|
  Authors$^1$^[Corresponding author: email@dfo-mpo.gc.ca], Other authors\n| $^1$Pacific Biological Station Fisheries and Oceans Canada, \n| Nanaimo, BC, Canada\n|
  $^2$Other addresses\n"
output:
    bookdown::pdf_document2:
      toc: false
      number_sections: false
      fig_caption: true
csl: ecological-applications.csl
bibliography: refs.bib
link-citations: yes
header-includes:
  \newcommand{\beginsupplement}{
  \setcounter{equation}{0}
  \renewcommand{\theequation}{S.\arabic{equation}}
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options:
  markdown:
    wrap: sentence
abstract: |
  Abstract here
---

@@

- Change in RE over time: To assess bias, we calculated the slope of a linear regression of RE by year.

>>>>

---
title: "Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation"
author: "|
  Sean C. Anderson$^1$^[Corresponding author: sean.anderson@dfo-mpo.gc.ca],
  Philina A. English$^1$,
  Other authors\n| $^1$Pacific Biological Station Fisheries and Oceans Canada, \n| Nanaimo, BC, Canada\n|
  $^2$Other addresses\n"
output:
    bookdown::pdf_document2:
      toc: false
      number_sections: false
      fig_caption: true
csl: ecological-applications.csl
bibliography: refs.bib
link-citations: yes
header-includes:
  \newcommand{\beginsupplement}{
  \setcounter{equation}{0}
  \renewcommand{\theequation}{S.\arabic{equation}}
  \setcounter{table}{0}
  \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0}
  \renewcommand{\thefigure}{S\arabic{figure}}}
editor_options:
  markdown:
    wrap: sentence
abstract: |
  Abstract here
---

@@

- Change in RE over time: to assess bias, we calculated the slope of a linear regression of annual RE by year and report it in units of proportional change by decade.
